---
title: "Wine Quality Dataset"
author: "ChunYu Lo (Jack), ChihChin Yang (Adela), Szu Wei Fu (Alexia)"
date: "4/18/2022"
output: powerpoint_presentation
---
```{r}
library(tidyverse)
library(GGally)
library(lattice)
library(ggfortify)
library(car)
```

```{r}
white_wine <- read.table(file = "winequality-white.csv",header = TRUE,sep=";") 
red_wine <- read.table(file = "winequality-red.csv",header = TRUE,sep=";")
```

## Problem Statement 


- The wine rating are subjective, we want to see whether we can use a physicochemical test to deduce sensory quality from those 11 variables
- The most important is to make wine rating more objective 

## Initial Hypotheses 

- Model assumption: E(Y)=β0 +β1X1 +β2X2 +...+β11X11 +ε 
- Initial Hypotheses:

H0: β1 =β2 =...=β11 =0
H1: βi ≠ 0 for some i =1,2,...11 

## Introduction

- Two kinds of data set, one is red wine and the other is white wine 
- The two sample sizes are not even, all variables are quantitative variables
- We would use different test to check the 1) Normality 2) Independence 3) Homogeneity

## White wine 
```{r}
str(white_wine)
```

## Red wine 
```{r}
str(red_wine)
```

## Input variables & Output variables

1. fixed acidity
2. volatile acidity
3. citric acid
4. residual sugar
5. Chlorides
6. free sulfur dioxide
7. total sulfur dioxide
8. Density
9. pH
10. Sulphates
11. alcohol
12. quality

## White wine 
```{r}
ggplot(gather(white_wine), aes(value)) +
  geom_histogram() +
  facet_wrap(~key, scales = "free")
```

## Red wine
```{r}
ggplot(gather(red_wine), aes(value)) +
  geom_histogram() +
  facet_wrap(~key, scales = "free")
```
Density and pH seems normally distributed 

Majority of other variables are skewed to the right 

## Red/White wine Quality Distribution
The dependent variable is discrete variable 

It was a continues integer and the rational number has meaning
```{r}
ggplot(white_wine, aes(quality))+
  geom_histogram()+
  ggtitle("White Wine Quality Distribution")
```

```{r}
ggplot(red_wine, aes(quality))+
  geom_histogram()+
  ggtitle("Red Wine Quality Distribution")
```

## White wine
```{r}
ggpairs(white_wine, title="White Wine Features Correlation with ggpairs")
```
The strongest association with quality is alcohol(0.436) 

The lowest association with quality are citric acid(-0.009) and free sulfur dioxide(0.008) 

## Red wine
```{r}
ggpairs(red_wine, title="Red Wine Features Correlation with ggpairs")
```
The strongest association with quality is alcohol(0.476) 

The lowest association with quality is residual sugar (0.014) 

## White wine
Therefore, 28% of the variability in quality is explained by the multiple linear regression with our reduced model which are eight variables.
```{r}
lm_white_wine <- lm(quality ~ ., data = white_wine) 
summary(lm_white_wine)
```

## Red wine
Therefore, 35% of the variability in quality is explained by the multiple linear regression with our reduced model which are seven variables. 
```{r}
lm_red_wine <- lm(quality ~ ., data = red_wine)
summary(lm_red_wine)
```

## White wine
```{r}
reduce_lm_white_wine <- step(lm_white_wine, direction = "both")
autoplot(reduce_lm_white_wine)
```

## Red wine
```{r}
reduce_lm_red_wine <- step(lm_red_wine, direction = "both")
autoplot(reduce_lm_red_wine)
```

## White/Red wine residual normality test
```{r}
shapiro.test(reduce_lm_white_wine$residuals)
shapiro.test(reduce_lm_red_wine$residuals)
```

## White/Red wine residual independence test
```{r}
durbinWatsonTest(reduce_lm_white_wine)
durbinWatsonTest(reduce_lm_red_wine)
```

## White/Red wine residual variance homogeneity test
```{r}
ncvTest(reduce_lm_white_wine)
ncvTest(reduce_lm_red_wine)
```

## Conclusion of Three Test

- With the small p-value which we reject the null hypothesis
- y does not conform to the normal distribution, 
- does not conform to the assumption of independence, 
- does not conform to the assumption of homogeneity. 

## Discussion 

- Although alcohol is the most powerful variable in wine quality. But it is risky to interpret the result as “more alcohol is the most powerful variable in wine quality”

- It would be better to interpret the result as adding more alcohol within the normal range that might improve the wine quality. 

## Future Directions 

- For future research, except for the physicochemical test, we can add more variables. For example, the year of the wine, grape varieties, price, etc. 

## References

Cortez, P. (2010, July). Data mining with neural networks and support vector machines using the R/rminer tool. In Industrial conference on data mining (pp. 572-583). Springer, Berlin, Heidelberg. 
Cortez, P., & Embrechts, M. J. (2013). Using sensitivity analysis and visualization techniques to open black box data mining models. Information Sciences, 225, 1-17. 
Lee, K., Lam, M., Pedarsani, R., Papailiopoulos, D., & Ramchandran, K. (2017). Speeding up distributed machine learning using codes. IEEE Transactions on Information Theory, 64(3), 1514-1529. 
Mei, S., & Zhu, X. (2015, February). Using machine teaching to identify optimal training-set attacks on machine learners. In Twenty-Ninth AAAI Conference on Artificial Intelligence. 
Moro, S., Cortez, P., & Rita, P. (2014). A data-driven approach to predict the success of bank telemarketing. Decision Support Systems, 62, 22-31. 
P. Cortez, A. Cerdeira, F. Almeida, T. Matos and J. Reis. Modeling wine preferences by data mining from physicochemical properties. In Decision Support Systems, Elsevier, 47(4):547-553, 2009. 
